Stochastic Newton with Arbitrary Sampling

### 2023-03-01 paper/main.tex
Added problem statement

\usepackage[utf8]{inputenc}
\usepackage[english, russian]{babel}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{amsmath, amsfonts, amssymb, amsthm, mathtools}

@@

	The problem is to minimize the empirical risk which has finite-sum structure \cite{kovalev2019stochastic}:
	\begin{equation}
		\underset{x \in \mathbb R^d}{\min} \left[ f(x) \overset{def}{=} \frac{1}{n} \sum \limits_{i=1}^n f_i(x) \right]
	\end{equation}
	where each $f_i$ is assumed to have Lipschitz Hessian. \\

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[english, russian]{babel}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{amsmath, amsfonts, amssymb, amsthm, mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{assumption}
\newtheorem{assumption}{Assumption}[section]

@@

	The problem is to minimize the empirical risk which has finite-sum structure \cite{kovalev2019stochastic}:
	\begin{equation}\label{ERM}
		\underset{x \in \mathbb R^d}{\min} \left[ f(x) \overset{def}{=} \frac{1}{n} \sum \limits_{i=1}^n f_i(x) \right]
	\end{equation}
	where each $f_i$ is assumed to have Lipschitz Hessian. \\

@@

\section{Problem statement}

	We discuss the problem of empirical risk minimization (ERM). The objective function $f$ (\ref{ERM}) is the average of a big number of functions $f_i$. In fact each $f_i$ is the loss on the $i$-th train data point. For example, this notation can be attributed to linear regression. In this case we try to fit the model's parameter vector $x$ to minimize the mean squared error (MSE) on the train data. \\

	\subsection{Assumptions}

	In our work we will assume the functions $f_i$ to satisfy the same regularity conditions that were originally introduced in \cite{kovalev2019stochastic}.

	\begin{assumption}[Strong convexity] A differentiable function $\phi:\ \mathbb R^d \rightarrow \mathbb R$ is $\mu$-strongly convex, where $\mu > 0$, if $\forall\ x, y \in \mathbb R^d$

	\begin{equation}\label{strong-conv}
		\phi(x) \geqslant \phi(y) + \langle \nabla \phi, x - y \rangle + \frac{\mu}{2} \| x - y \|^2,
	\end{equation}
	\end{assumption}
	where the norm $\| \cdot \|$ is Euclidean. For twice differentiable functions this assumption is equivalent to the Hessian having each eigenvalue $\geqslant \mu$.

	\begin{assumption}[Lipschitz Hessian] A function $\phi: \mathbb R^d \rightarrow R$ has H-Lipschitz Hessian if $\forall\ x, y \in \mathbb R^d$

	\begin{equation}\label{lip-hess}
		\| \nabla^2 \phi(x) - \nabla^2 \phi(y) \| \leqslant \| x - y \|
	\end{equation}
	\end{assumption}

	\subsection{Sampling}

	\begin{definition}[Sampling]
		A random set-valued mapping $\hat S:\ [n] \rightarrow 2^{[n]}$ is called sampling.
	\end{definition}

	That means that each $S_k \subseteq [n]$ is a realization of $\hat S$. In this case we can call any particular probability distribution on $2^{[n]}$ a sampling strategy.
	\subsection{Algorithm}

	We will be applying different sampling strategies for the Algorithm 1 from \cite{kovalev2019stochastic}:

	\begin{algorithm}
		\caption{Stochastic Newton (SN)}\label{SN}
		\begin{algorithmic}
			\item \textbf{Initialize:} Choose starting iterates $w_1^0, w_2^0, ... w_n^0 \in \mathbb R^d$

			\item \For {$k = 0, 1, 2, ...$}

				$ x^{k+1} = \left[ \frac{1}{n} \sum \limits_{i=1}^n \nabla^2 f_i(w_i^k) \right]^{-1} \left[ \frac{1}{n} \sum \limits_{i=1}^n \nabla^2 f_i(w_i^k) w_i^k - \nabla f_i(w_i^k) \right] $

				Choose a subset $S^k \subseteq \{ 1, 2, ..., n \}$ with one of the sampling strategies

				$w_i^{k+1} = 
				\begin{cases}
					x^{k+1} & i \in S^k \\
					w_i^k & i \notin S^k
				\end{cases}$

			\item \EndFor
		\end{algorithmic}
	\end{algorithm}

	\subsection{Goal of the project}

	We aim to explore different sampling strategies for the Algorithm \ref{SN} in order to obtain practical improvements and their theoretical explainations.
